---
title: "Session 1 - Practice 1"
author: "Your Name Here | and your email address"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Session 1 Practice 1

## Overview 
Lets start our R adventure by getting familar with the enviorment. This is a notebook you can create a new notebook by simply doing "File > New File > R Notebook". Once you have a new notebook just select Run > Run All and see what happens. 

In this notebook we'll perform the following 
1. load the tidyverse library - you can install it by dong install.packages("tidyverse") or by clicking Packages > Install 
2. use R as a calculator 
3. get familar with assignment operator <- 
4. import a dataset 
6. create a basic chart 
7. knit your notebook 

## Libraries 

Tasks: copy the following into the code block below, then run the code block by clicking the green triangle in the block

library(tidyverse)

```{r}


```

## Use R as a Calculator 

Tasks: perform the following 

1. 10 + 10 
2. 5 - 10
3. 3 * 20 
4. we'll create some variables using the assingment operator <- 
  number_5 <- 5
  number_10 <- 10 
  number_5 * number_10 
5. create an expression that adds 10 to 3 times 5 

```{r}

```

## Get Familar with the Assignment Operator 

Tasks: 
1. create a new variable "str_variable" and assign it using <- the value "new variable" 
  str_variable <- "new variable"
2. create a two varibles first_name and last_name assign them your first and last name 
3. use the paste function to create a new variable full_name 
  full_name <- paste(first_name, last_name)

```{r}

```

### Do some Comparisons 

Tasks: 
1. is 5 > 10? 
2. is 10 > 5 
3. copy and paste the following and run it. 

number_5 <- 5 
number_10 <- 10 

IF (number_5 < number_10) {
  print("5 is less than 10")
}

4. create a IF statement that compares 7 X 10 is less than 10 X 10 print the value of 10 * 10 

```{r}

```

### FOR Loop 

Task: you are given a vector of years we want to loop through the years to do this copy and paste the following into the code block

list_o_years <- c(2013, 2014, 2015, 2016, 2019, 2020 )

for (y in list_o_years) { 	
  print(paste("The year:", y)) 

}

add 2021 to the vector of years, does it matter where you put it? 


```{r}


```

## Import a Dataset 

We use the read_csv() functionto read a CSV file into a data frame. copy and paste the code below into a code block 

msft <- read_csv("data/MSFT.csv")
head(msft,10)

```{r}

```

## Make a Chart 

Task: make a histogram of Volume by copying, pasting and running the code below. 

1. first we'll use the old style hist() function to make a histogram that looks like it came from 1980

hist(msft$Volume)

2. next we'll use gglot() function to make a histogram 

options(scipen = 999) # turn off scientific notation 

ggplot(msft, aes(x=Volume))+
geom_histogram(bins=50) +
labs(title="MSFT Volume", x="Freq Count", y="Volume")


```{r}

```


## Finally Knit

Kniting runs your notebook from top to bottom in a separate session and produces a nice looking formatted report. Above select Knit > Knit to HTML this will produce a html file which you can open in your browser. 
